### 2018-05-28 write-up/ott_spec.tex
Fix many small writing errors

The following pages present a specification of the grammar and type-system used
by my project, produced using the Ott~\cite{sewell_ott} tool. It is important to note
that the type-system described here is not how it is implemented: it is easier
and clearer to describe the system as below for explaining. However, for implementing,
I found it much more and user- and debugging-friendly to:

@@

    \item Implement it so that the type-environment \emph{changes} as a result
        of type-checking an expression, similar to the rules shown in
        Figure~\ref{fig:example_rules}; with this, the below semantics describe
        the \emph{difference} between the environment after and before checking
        an expression. For example, in the pair-introduction rule, $\Gamma =
        \Gamma_2 - \Gamma_1$ and $\Gamma' = \Gamma_3 - \Gamma_2$, for an
        appropriate definition of $(-)$.

@@

    \item Have \emph{one} environment where variables were \emph{tagged} as
        linear and unused, linear and used, and intuitionistic. This was
        definitely an implementation convenience so that variable binding could
        be handled uniformly for linear and intuitionistic variables and
        scoping/variable look-up could be handled implicitly thanks to the
        associative-list structure of the environment. So, the variable
        rule would most accurately look like:
        \begin{prooftree}
            \AxiomC{}
            \RightLabel{\textsc{Ty\_Var}}
            \UnaryInfC{$\Theta; \Gamma, x \overset{n}{:} t \vdash x : t ; \Gamma, x \overset{n-1}{:} t$}
        \end{prooftree}
        for $n \in \{0\,\textrm{(used)}, 1\,\textrm{(unused)},
        \omega\,\textrm{(intuitionistic)}\}$, $\omega - 1 = \omega$ and  $1 - 1 = 0$.

>>>>

The following pages present a specification of the grammar and type system used
in LT4LA, produced using the Ott~\cite{sewell_ott} tool. It is important to
note that the type system is not implemented how it is described in the coming
pages.  For explaining (and using Ott) it was easier to set it out as below.
However, for implementing, I found it much more and user- and
debugging-friendly to:

@@

    \item Have the type environment \emph{change} as a result
        of type-checking an expression, similar to the rules shown in
        Figure~\ref{fig:example_rules}; with this, the below rules describe
        the \emph{difference} between the environment after and before checking
        an expression. For example, in the pair-introduction rule, $\Gamma =
        \Gamma_2 - \Gamma_1$ and $\Gamma' = \Gamma_3 - \Gamma_2$, for an
        appropriate definition of $(-)$.

@@

    \item Have \emph{one} environment where variables were \emph{tagged} as
        linear and unused, linear and used, and intuitionistic. This was
        definitely an implementation convenience so that variable binding could
        be handled uniformly for linear and intuitionistic variables and
        scoping/variable look-up could be handled implicitly with the
        associative-list structure of the environment. So, it would be more
        (but still not completely) accurate to define the variable rule as:
        \begin{prooftree}
            \AxiomC{}
            \RightLabel{\textsc{Ty\_Var}}
            \UnaryInfC{$\Theta; \Gamma, x \overset{n}{:} t \vdash x : t ; \Gamma, x \overset{n-1}{:} t$}
        \end{prooftree}
        for $n \in \{0\,\textrm{(used)}, 1\,\textrm{(unused)},
        \omega\,\textrm{(intuitionistic)}\}$, $\omega - 1 = \omega$ and  $1 - 1 = 0$.
